Prefetching SPARQL query cacher

### 2016-07-28 dissertation/cache-proxy.tex
Add some substructure Add appendix and move modules and stuff there
Note that @kasei would have been a co-author of a paper

@@

@@

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. To
install the system on the top of a Debian system with only essential
packages requires 146 Debian packages. Running the test suite requires
even more. As such, it builds on the code of hundreds of authors, too
many to enumerate. I shall constrain myself to list the modules that
have code that has been motivated by this study. Modules that have
other primary authors than myself have been started prior to this
present project, but may have substantial contributions from this
project. The Attean framework was started as part of the effort in
Section~\ref{sec:conpush}, but even though it has been developed
further with the requirements that arose from this project and has
contributions from me, the vast majority of the code has been written
by Gregory Todd Williams. The main work in this project has gone into
the module \pmodule{AtteanX::Query::Cache}, where I have authored the
vast majority of the code. The relative difference in authorship can
be further examined by checking the linked Github repositories, or by
using git2prov\footnote{See \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol. The system is further detailed in the following sections:

@@

>>>>

\subsection{Scenario}

@@

\subsection{Key Problems}

@@

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. For
a detailed account of the modules that are a part of the system and
the authors that have contributed code in this ecosystem, see
Appendix~\ref{app:modules}.

@@

\begin{subappendices}
%\renewcommand{\setthesection}{\Alph{section}}
%\renewcommand{\setthesubsection}{\Alph{subsection}}

%\section{Appendix}
\section{Appendix: Modules and Their Contributors}\label{app:modules}

To install the system on the top of a Debian system with only
essential packages requires 146 Debian packages. Running the test
suite requires even more. As such, it builds on the code of hundreds
of authors, too many to enumerate. I shall constrain myself to list
the modules that have code that has been motivated by this
study. Modules that have other primary authors than myself have been
started prior to this present project, but may have substantial
contributions from this project. The Attean framework was started as
part of the effort in Section~\ref{sec:conpush}, but even though it
has been developed further with the requirements that arose from this
project and has contributions from me, the vast majority of the code
has been written by Gregory Todd Williams, who would have been a
co-author of this work had it been published in the peer-reviewed
literature. The main work in this project has gone into the module
\pmodule{AtteanX::Query::Cache}, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{See \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol.

\end{subappendices}
